GVN-Hoist: Hoisting Computations from Branches

### 2016-08-08 hoist.tex
calls

\subsubsection{Hoisting calls}
Currently we hoist all the calls.

\subsection{Making the transformation}
Putting a copy of the computation at the hoisting point and removing all the
computations made redundant by the new copy.

>>>>

\subsubsection{Hoisting calls}
Currently we hoist all the calls that are suitable candidates for hoisting.

\subsection{Making the transformation}
Once all the legality checks and profitability checks are satisfied, a copy of
the computation is inserted at the hoisting point and all the computations made
redundant by the new copy are removed. After that SSA semantics is restored by
updating the intermediate representation (IR) to reflect changes.
